Supplementary Materials

### 2020-06-18 analysis/analysis.Rmd
Moving SessionInfo to the end
parameteric orientations

# Loading packages and importing data

##  Packages

@@

## Import Data

@@

### EEG Data

@@

```{r cache=TRUE, fig.cap = "Data are the root-mean-squaured (rms) over the odd-harmonic filtered waveforms."}
d_eeg %>% ggplot(aes(x = rms)) + 
    geom_histogram(binwidth = 0.2, fill = "skyblue", colour = "black") +
    theme_lucid()
```

### Threshold Data

@@

### Control Data

@@

### Types of Symmetry

@@

### Subgroup Relationships
Import subgroup information and display a table of the relationships that we will be investigating.

@@

@@

summary(my_models$eeg)

@@

>>>>

# Importing data

@@

@@

## EEG Data

@@

```{r cache=TRUE, fig.cap = "Data are the root-mean-squaured (rms) over the odd-harmonic filtered waveforms."}
d_eeg %>% ggplot(aes(x = rms)) + 
    geom_histogram(binwidth = 0.2, fill = "skyblue", colour = "black") +
    theme_lucid()
```
```{r}

d_eeg %>% filter(wg %in% c("P2", "P3", "P4", "P6")) %>% ggplot(aes(x = wg, y = log(rms))) + geom_boxplot(notch = T)

d_eeg %>% group_by(wg) %>% summarise(
  mean_log_rms = mean(log(rms)),
  sd_log_rms = sd(log(rms)),
  median_log_rms = median(log(rms)))

## Threshold Data

@@

## Control Data

@@

## Types of Symmetry

@@

## Subgroup Relationships
Import subgroup information and display a table of the relationships that we will be investigating.

@@

Will try fitting a new parametric model on rotations

```{r}

d_eeg %>% filter(wg %in% c("P2", "P3", "P4", "P6")) %>%
  mutate(orientation = parse_number(wg))-> d_eeg_rot

m_eeg_rot <- brm(data = d_eeg_rot, rms ~ orientation + (1|subject), family = "lognormal")

d_eeg_rot %>% modelr::data_grid(orientation) %>%
  add_fitted_draws(m_eeg_rot, re_formula = NA, n=200) %>%
  ggplot() + 
  geom_line(data = d_eeg_rot, aes(x = orientation, y = rms, group = subject), alpha = 0.1, colour = "darkred") +
  geom_path(aes(x = orientation, y = .value, group = .draw), alpha = .2, colour = "thistle4") + 
  theme_minimal() 
```

@@

@@

# Package and Session Information
